\documentclass[11pt]{article}
\parindent 0px
\usepackage{hyperref}

\title{MY \LaTeX\ DOC}
\author{Zahra Sadeghi}
\date{\today}
\begin{document}
\tableofcontents
\maketitle

This will produce \textit{italicized} text.\\
This will produce \textbf{bold face} text.\\
This will produce \textsc{small caps} text.\\
This will produce \texttt{typewriter font} text.\\
You can see the rankings of world university at \url{https://www.topuniversities.com/world-university-rankings}

You can see the rankings of world university at \href{https://www.topuniversities.com/world-university-rankings}{QS Universities Rankings}

\vspace{1cm}


Changing the size of text :
\begin{enumerate}
\item normal size :
\begin{normalsize}This text has a normal size.\end{normalsize}
\item large size :
\begin{large}This text has a large size.\end{large}
\item larger size :
\begin{Large}This text has a larger size.\end{Large}
\item huge size :
\begin{huge}This text has a huge size.\end{huge}
\item huger size :
\begin{Huge}This text has a huger size.\end{Huge}
\item normal size :
This text has a normal size.
\item small size :
\begin{small}This text has a small size.\end{small}
\item script size :
\begin{scriptsize}This text has a script size.\end{scriptsize}
\item tiny size :
\begin{tiny}This text has a tiny size.\end{tiny}
\end{enumerate}

\pagebreak

Justifying:


\begin{center}This line is centered.\end{center}

\begin{flushleft}This line is left-justified.\end{flushleft}

\begin{flushright}This line is right-justified.\end{flushright}

\vspace{1cm}

%\tiny  commenting
This line is centered.

This line is left-justified.

This line is right-justified.


\section{Linear Functions}
	\subsection{Slope-Intercept Form}
		\subsubsection{Example 1:}
		\subsubsection{Example 2:}
	\subsection{Standard Form}
	\subsection{Point-Slope Form}
\section{Quadratic Functions}
	\subsection{Vertex Form}
	\subsection{Standard Form}
	\subsection{Factored Form}





\end{document}